Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-27 Report/dual_approach.tex
submitted

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step. We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}

>>>>

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, it is still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange between the coupling \acp{BS}, the distributed schemes are often iterated for a limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step. We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-27 Report/mse_formulation.tex
submitted

In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}

>>>>

In all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}. This follows from the fact that  \eqn{\beta_{l,k,n}} can take any value by satisfying \eqref{eqn-6.3} without violating the constraints of problem \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
